### 2014-11-13 tex/evaluation.tex
adding the evaluation

    \hline
  \end{tabular}}
  \caption{Comparing the efficiency of the summary heap appraoch to GSE and Lazier\# algorithms.}
  \label{tab:results}
\end{table*}
%\end{figure*}

@@

The results of the experiments are presented in Table
\ref{tab:results}. Each row contains the results for the specified $k$-bound 
for each artifact evaluated. The columns show the total
wall clock time in seconds, states explored, and paths generated for
each of the algorithms. The headings \gsetxt{}, L\#, and SL correspond
to the Generalized Symblic Execution, lazier\#, and \symtxt{}
algorithms, respectively. Note that we do no present the results for
the lazier algorithm since they are almost identical to that of lazier\#
for our examples. Table entries containing '-' correspond to test runs
that exceeded the allotted time bound of 10 minutes.

@@

Curiously, the pattern established with run-times and path counts does
not hold true for state counts. State counts can vary between
algorithms because states in JPF represent points of nondeterminism,
and each algorithm differs in this regard. For example, \gsetxt{} has
additional points of nondeterminism during field reads, but in
contrast reference compares are completely deterministic. Thus, in
example programs with large numbers of reference compares, such as
TreeMap, state counts for lazier\# and the \symtxt{} algorithm may exceed those for
\gsetxt{}. The larger state count, however, does not contribute to the
runtime of the technique.

>>>>

    \hline
  \end{tabular}}
  \caption{Comparing the efficiency of the summary heap approach to GSE and Lazier\# algorithms.}
  \label{tab:results}
\end{table*}
%\end{figure*}

@@

The results of the experiments are presented in Table
\ref{tab:results}. Each row contains the results for the specified $k$-bound 
for each artifact evaluated. The columns show the total
wall clock time in seconds, states explored, and paths generated for
each of the algorithms. The headings \gsetxt{}, L\#, and SL correspond
to the Generalized Symbolic Execution, lazier\#, and \symtxt{}
algorithms, respectively. Note that we do no present the results for
the lazier algorithm since they are almost identical to that of lazier\#
for our examples. Table entries containing '-' correspond to test runs
that exceeded the allotted time bound of 10 minutes.

@@

The number of states varies between algorithms, for example, \gsetxt{}
has additional points of nondeterminism during field reads, but in
contrast reference compares are completely deterministic. Thus, in
example programs with large numbers of reference compares, such as
TreeMap, state counts for lazier\# and the \symtxt{} algorithm may
exceed those for \gsetxt{}. We observed that the additional states
generated by the summary heap algorithm are unsatisfiable at the point
of reference compares; this is why they do not contribute any
additional branches in the final symbolic execution tree. Furthermore,
the larger state count does not impact the overall runtime of the
technique.

%The additional states generated by summary heap are unsatisfiable
%which is why they do not add nodes in the final symbolic execution
%tree. Furthermore, the larger state count does not impact the overall
%runtime of the technique.
